---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# shutterstock

[![CRAN status badge](https://www.r-pkg.org/badges/version/shutterstock)](https://cran.r-project.org/package=shutterstock)

> R library for Shutterstock REST API

## Installation

You can install the released version of shutterstock from
[CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("shutterstock")
```

You can also install development version with
`devtools::install_github("strboul/shutterstock")`.

## Authenticate with OAuth 2.0

OAuth 2.0 authentication is better to use as its scope is greater than the
capabilities of the basic authentication.

A general use of `.Renviron` is to store API keys. Client Id and secret can be
get after registering the app. Shutterstock API requires to define the callback
URL explicitly. For instance, if you set your Callback URL as
`http://localhost:3000/auth/shutterstock/callback/` then the hostname should
be set as `localhost`.

Add the following variables to the file (be sure the values are in quotes):

```
SHUTTERSTOCK_CLIENT_ID="<enter-your-client-key>"
SHUTTERSTOCK_CLIENT_SECRET="<enter-your-client-secret>"
SHUTTERSTOCK_CALLBACK_URL="<enter-your-callback-url>"
```

Don't forget to restart your environment. Check `sstk_keys()` to see if the
variables are properly set up. Please read the 
[OAuth 2.0 guide](https://developers.shutterstock.com/oauth-20) throughly.

## Examples

Search images:
```{r search_images, eval = FALSE}
today <- as.character(Sys.Date())
searchImages(query = "farmer", sort = "popular", added_date = today)
```

## LICENSE

MIT
