---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library("shutterstock")
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "##",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# shutterstock

[![Travis build status](https://travis-ci.org/strboul/shutterstock-r.svg?branch=master)](https://travis-ci.org/strboul/shutterstock-r) [![CRAN status badge](https://www.r-pkg.org/badges/version/shutterstock)](https://cran.r-project.org/package=shutterstock) [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/shutterstock)](https://www.r-pkg.org/pkg/shutterstock) [![Coverage status](https://codecov.io/gh/strboul/shutterstock-r/branch/master/graph/badge.svg)](https://codecov.io/github/strboul/shutterstock-r?branch=master)

R library for Shutterstock REST API. Please refer to the official reference
[here](https://api-reference.shutterstock.com/).

## Installation

<!--You can install the released version of shutterstock from
[CRAN](https://CRAN.R-project.org) with:
``` r
install.packages("shutterstock")
```-->

You can install development version:
```r
# install.packages("devtools")
devtools::install_github("strboul/shutterstock")
```

## Usage

Search the most popular images about *Amsterdam*:

```{r, eval = TRUE}
library("shutterstock")
amsterdam <- searchImages(query = "Amsterdam", sort = "popular")
d <- amsterdam[["data"]]
do.call(rbind, lapply(d, function(x) {
  data.frame(
    id = x[["id"]],
    description = paste(strtrim(x[["description"]], 35L), "..."), # truncate description field
    preview = x[["assets"]][["preview"]][["url"]],
    stringsAsFactors = FALSE
  )
})) -> popular
head(popular)
```

Build a frequency plot from keywords of the images searched with a *family* query:

```{r}
library("ggplot2")

images <- searchImages(query = "family", per_page = 225)
# extract image ids:
image.ids <- sapply(seq_along(images[["data"]]), function(i) {
  images[["data"]][[i]][["id"]]
})

data <- lapply(image.ids, function(x) {
  cat(sprintf("[%s] get image: \"%s\"", match(x, image.ids), x), sep = "\n")
  Sys.sleep(4) # try to prevent HTTP 429 error
  details <- getImageDetails(id = x)
  as.character(details[["keywords"]])
})

kws <- do.call(c, data)
tbl.counts <- as.data.frame(table(kws))
top.tbl <- tbl.counts[order(tbl.counts["Freq"], decreasing = TRUE), ]
top <- head(top.tbl, 15L)

ggplot(top, aes(x = kws, y = Freq)) +
  geom_bar(stat = "identity", width = 0.7, color = "black", fill = "white") +
  labs(title = "The most popular family keywords", x = "Keyword") +
  ylab(NULL) +
  theme_bw()
```
```{r plot, eval = TRUE, echo = FALSE, out.width = "75%", out.height = "75%"}
library("ggplot2")
# use pre-computed data for easy demonstration:
top <- structure(list(kws = c("family", "father", "people", "mother", 
"happy", "child", "together", "girl", "daughter", "man", "woman", 
"young", "fun", "lifestyle", "boy"), Freq = c(212L, 191L, 190L, 
188L, 183L, 174L, 161L, 155L, 148L, 146L, 145L, 134L, 131L, 117L, 
113L)), row.names = c(493L, 515L, 1064L, 973L, 660L, 271L, 1452L, 
601L, 377L, 921L, 1587L, 1600L, 578L, 861L, 187L), class = "data.frame")
# the same plot as above:
ggplot(top, aes(x = kws, y = Freq)) +
  geom_bar(stat = "identity", width = 0.7, color = "black", fill = "white") +
  labs(title = "The most popular family keywords", x = "Keyword") +
  ylab(NULL) +
  theme_bw()
```

## OAuth 2.0 Authentication

OAuth 2.0 authentication is better to use for the queries as its scope is
greater than the capabilities of the basic authentication. Read the vignette for
more information. For general OAuth problems, please read the [Shutterstock OAuth 2.0 guide](https://api-reference.shutterstock.com/#authentication-oauth-authentication-h2) thoroughly.

## Development

PRs are welcomed!

Only `GET` methods are supported in the current version.

See `?shutterstock` package documentation for more information. 

Please note that the 'shutterstock' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
